Windowed Developer Topic Analysis

### 2009-03-14 lda-paper.tex
more changes to intro
lda paper

abram

  In this lab report we seek to explore how topics shift over time in
  the source control repository of a project. We analyze commit
  comments, and even source code per revision per each time window and
  extract the topics prevelant in that window. We expect that topic
  sets will change over time and the change in topic sets indicate a
  change in the focus of development. We suppose this could help us to
  segment the revisions on the time line to discover parts of an
  iteration. For topic extraction we use \lda (LDA).

@@

What happened in the previous iteration? What were the developers
working on? What was the developer in the next cubicle working on?
What were the common topics and issues dealt with in the current
release of the software? What were the topics of the previous release?

@@

\section{Previous Work}

>>>>

%   In this lab report we seek to explore how topics shift over time in
%   the source control repository of a project. We analyze commit
%   comments, and even source code per revision per each time window and
%   extract the topics prevelant in that window. We expect that topic
%   sets will change over time and the change in topic sets indicate a
%   change in the focus of development. We suppose this could help us to
%   segment the revisions on the time line to discover parts of an
%   iteration. For topic extraction we use \lda (LDA).

@@

What happened in the previous iteration? What were the developers
working on? What was the developer in the next cubicle working on?
What were the common topics and issues dealt with in the current
release of the software? What were the topics of the previous release?
Given the requirements agreed to at the start of the iteration did our
developers work on them? What else did they work on. Were there issues
which were orthogonal to the

Topic analysis, with respect to Software Control Systems (SCSs), is
valuable as it has many uses for the stakeholders involved.

Example scenarios where the usage of this technique would prove useful
are numerous. Imagine a development team has agreed to implement some
features at the start of an iteration. By the end of the iteration
only some of the agreed upon features are implemented. The developers
swear they were focusing solely on the features agreed upon. Topic
analysis could help by teasing out the distinct topics or focusses of
the developers. Perhaps the developers had to deal with issues
orthogonal to the features they were working on, but were probably
necessary to complete such features. Developers might have grouped
those orthogonal changes into one of the features and might not

@@

\section{Background}

Some terms we will be using for the rest of the paper include:
message, word distribution, topic and trend. Messages are block of
text written by developers, in this paper messages will be the CVS
commit comments. Word distributions are the summary of a message by
word count, effectively the word distribution will be over all
messages looked at but since most words will not appear in a message,
a word distribution is effectively a word count divided by the message
size. A topic is a unique word distribution, but effectively a set of
words unique to an independant behaviour in the text corpus, in this
paper we often summarize topics by their top 10 more frequent words.
A trend is a one or more similar topics which reoccur over
time. Trends are important because they are sets of topics which
reoccur over the development of a project.
